---
title: "Comparing Native Lamprey and Sea Lamprey"
output:
  html_document:
    df_print: paged
---


This data file will show the results of across-species PCA and genetic trees on each sea lamprey (PM) stream and test samples of American (LA) and Northern Brook lamprey (IF). The SNPs used to differentiate populations were SNPs location at Rapture targeted loci with over 95% of individuals genotyped in either sea lamprey or native lamprey. The initial PCA and tree was tested on a random sample of 30 sea lamprey individuals across locations:


###Test Data Set to generate PCA: 
```{r,echo=F,message=FALSE}
library(tidyverse)
library(adegenet)
library(ape)
load("PCAData/genlight_pca_test.RData")

#run PCA
pca <- glPca(snp,nf = 10)
#set colors for plot
locs <- data.frame(ID=snp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(snp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Bad River (BAD)
```{r,echo=F,message=FALSE}
load(file = "PCAData/genlight_pca_all.RData")
LA <- snp[grep("LA",snp@ind.names),]
IF <- snp[grep("IF",snp@ind.names),]
PM <- snp[grep("BAD",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Betsie River (BEI)
```{r,echo=F,message=FALSE}
PM <- snp[grep("BEI",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Betsy River (BET)
```{r,echo=F,message=FALSE}
PM <- snp[grep("BET",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Brule River (BRL)
```{r,echo=F,message=FALSE}
PM <- snp[grep("BRL",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Cattaraugus River (CAT)
```{r,echo=F,message=FALSE}
PM <- snp[grep("CAT",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Cheboygan River (CHE)
```{r,echo=F,message=FALSE}
PM <- snp[grep("CHE",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###East Au Gres River (EAG)
```{r,echo=F,message=FALSE}
PM <- snp[grep("EAG",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Ford River (FOR)
```{r,echo=F,message=FALSE}
PM <- snp[grep("FOR",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Little Two-Hearted River (TWO)
```{r,echo=F,message=FALSE}
PM <- snp[grep("TWO",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Manistee River (MAN)
```{r,echo=F,message=FALSE}
PM <- snp[grep("MAN",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Manistique River (MAI)
```{r,echo=F,message=FALSE}
PM <- snp[grep("MAI",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Middle River (MIR)
```{r,echo=F,message=FALSE}
PM <- snp[grep("MIR",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Misery River (MIS)
```{r,echo=F,message=FALSE}
PM <- snp[grep("MIS",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Muskegon River (MUS)
```{r,echo=F,message=FALSE}
PM <- snp[grep("MUS",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Ocqueoc River (OCQ)
```{r,echo=F,message=FALSE}
PM <- snp[grep("OCQ",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Sterling River (STE)
```{r,echo=F,message=FALSE}
PM <- snp[grep("STE",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Swan Creek (SWN)
```{r,echo=F,message=FALSE}
PM <- snp[grep("SWN",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```

###Tahquamenon River (TAQ)
```{r,echo=F,message=FALSE}
PM <- snp[grep("TAQ",snp@ind.names),]
tmp <- rbind(LA,IF,PM)
locs <- data.frame(ID=tmp@ind.names)
locs <- locs %>% separate(ID, into = c("spp","loc","indiv"),sep = "_") %>% select(spp)
locs$col <- NA
for(i in 1:length(locs$spp)){
  if(locs$spp[i] == "LA"){locs$col[i] <- "blue"}
  if(locs$spp[i] == "IF"){locs$col[i] <- "dark green"}
  if(locs$spp[i] == "PM"){locs$col[i] <- "purple"}
}
pca <- glPca(tmp,nf=10)

#plot PCA
par(mfrow=c(1,2))
plot(pca$scores[,1], pca$scores[,2],
     col=locs$col,cex=0.5)
plot(pca$scores[,1], pca$scores[,3],
     col=locs$col,cex=0.5)

#construct tree
tre <- nj(dist(as.matrix(tmp)))
#plot tree
plot(tre, typ="fan", cex=0.7)
```
